B\'{e}zier $\bar{B}$ projection

### 2018-01-26 projection1120.tex
fixed refernces

The element-wise projection produces one control value for each element in the support of the function.  These values must be combined in order to provide the final control value.  A core component of the B\'ezier projection algorithm is the definition of an appropriate averaging operation.  A weighted average of the values is computed using the weighting
\begin{equation}\label{eqn:Bezier_weight}
\omega_a^e=\dfrac{\int_{\Omega^e} N_{a}^e \, d\Omega}{\int_{\Omega^A} N_{A(e,a)} \, d\Omega}
\end{equation}
where $\Omega^e$ corresponds to the physical domain of element $e$, $A(e,a)$ is a mapping from a local nodal index $a$ defined over element $e$ to a corresponding global node index $A$, and $\Omega^A$ corresponds to the physical support of $N_A$. The final averaged global control point is then calculated as
\begin{equation}
P_A=\sum_{\Omega^e\in \Omega^A } \omega_{A(e,a)} P_{A(e,a)}.
\end{equation}
B\'ezier projection onto NURBS functions can be defined in an analogous manner~\cite{thomas_bezier_2015}.

@@

\item{Step 3:} Each cluster of control points is averaged to obtain a
  single control point by weighting each point in the cluster according
  to the weighting given in (\ref{eqn:Bezier_weight}). The resulting control
  points are shown as circles with the relative contribution from each
  element to each control point indicated by the colored fraction of the
  control point marker. e colors in Figures~\ref{fig:weights} and~\ref{fig:loc-proj-example} are coordinated
  to illustrate where the averaging weights come from and their values.
\end{description}

@@

We have demonstrated the performance of the approach in the context of shear deformable beams (to alleviate transverse shear locking) and nearly incompressible elasticity problems (to alleviate volumetric locking). The proposed method reduces locking errors and achieves (nearly) optimal convergence rates \added{ for the symmetric method and optimal rates for the non-symmetric method}. The cases where optimal rates were not achieved \added{when using the the symmetric formulation are a symptom of the fact that the symmetric formulation (is not consistent with the mixed formulation) has may not satisfy the inf-sup condition}.

>>>>

The element-wise projection produces one control value for each element in the support of the function.  These values must be combined in order to provide the final control value.  A core component of the B\'ezier projection algorithm is the definition of an appropriate averaging operation. \added{The process of computing weights is illustrated in Figure~\ref{fig:weights}.} A weighted average of the values is computed using the weighting
\begin{equation}\label{eqn:Bezier_weight}
\omega_a^e=\dfrac{\int_{\Omega^e} N_{a}^e \, d\Omega}{\int_{\Omega^A} N_{A(e,a)} \, d\Omega}
\end{equation}
where $\Omega^e$ corresponds to the physical domain of element $e$, $A(e,a)$ is a mapping from a local nodal index $a$ defined over element $e$ to a corresponding global node index $A$, and $\Omega^A$ corresponds to the physical support of $N_A$. The final averaged global control point is then calculated as
\begin{equation}
P_A=\sum_{\Omega^e\in \Omega^A } \omega_{A(e,a)} P_{A(e,a)}.
\end{equation}
B\'ezier projection onto NURBS functions can be defined in an analogous manner~\cite{thomas_bezier_2015}.

@@

\item{Step 3:} Each cluster of control points is averaged to obtain a
  single control point by weighting each point in the cluster according
  to the weighting given in (\ref{eqn:Bezier_weight}). The resulting control
  points are shown as circles with the relative contribution from each
  element to each control point indicated by the colored fraction of the
  control point marker. Colors in Figures~\ref{fig:weights} and~\ref{fig:loc-proj-example} are coordinated
  to illustrate where the averaging weights come from and their values.
\end{description}

@@

We have demonstrated the performance of the approach in the context of shear deformable beams (to alleviate transverse shear locking) and nearly incompressible elasticity problems (to alleviate volumetric locking). The proposed method reduces locking errors and achieves (nearly) optimal convergence rates \added{ for the symmetric method and optimal rates for the non-symmetric method}. The cases where optimal rates were not achieved \added{when using the the symmetric formulation are a symptom of the fact that the symmetric formulation is not consistent with the mixed formulation}.
